\documentclass{article}

\usepackage{amssymb}
\usepackage{amsmath}

\title{ME699 Final Project Proposal}
\date{02-04-2020}
\author{Benton Clark, Ethan Howell, Brian Moberly}

\begin{document}
\pagenumbering{gobble}
\maketitle

\section{Project Outline}
For our project, we are proposing three primary phases:

\begin{itemize}
  \item Modeling
  \item Perception and Planning
  \item Control
\end{itemize}

\noindent Each phase of the project will feed into the next.
For instance, the model designed in the robotic modeling section will then be
used in the control section of the project.
By the end of the project, our goal is to have a fully modeled, controlled
robotic manipulator capable of following a simple trajectory and moving to
desired target locations in task space to accomplish simple goals.

\section{Demonstration}
The end goal of our project is to apply the modeling, perception and adaptive
controls to the Panda Robot arm.
The task will consist of the arm beginning in a configuration, moving towards an
intermediate state where an object is located, picking up that object, and
successfully moving that object to a desired goal state.
The object will be of unknown and variable mass, meaning the arm must be able to
effectively adapt to objects of differing weight online.
The exact location of the object must also be identified by the ``camera''
attached to the Panda, meaning a valid path must be found to both reach the
object and take it to the goal state.
The goal state will be fixed.

For the modeling portion, both static free and dry friction models will be used.
The perception and planning portion will be tasked with filtering out small
amounts of Gaussian white noise from both the joint configurations and the
camera readings in task space.
It must also find a valid trajectory of configurations in both task and joint
space to complete the objective.
The adaptive controller will use both the modeling and perception values in
determining the joint torques to command to follow the given trajectory.
It will also compensate for the additional weight on the last link of the arm
when the object of unknown mass is picked up.

\input{benton.tex}
\input{brian.tex}
\input{ethan.tex}

\section{Team Contributions}
For the individual sections of the project, Benton will focus on the robotic
modeling, Ethan on the robotic controls, and Brian on the perception and
tracking.
However, since each part of the project will slowly feed into one another, each
team member will help contribute to all three parts of the project equally.

\end{document}
